SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/data.tex
Edit data section.

Analysed texts, in addition to the raw text, contain more detailed annotations including parts of speech, morphological information, and syntactic relations.  This is stored as a table, where rows represent words, and columns represent the following types of information: document ID, language code, sentence ID, word ID, wordform, lemma, morphological information, part of speech, gloss, head/governor, and relation/role.

@@

Our resulting corpus runs the full gamut of text types outlined by Abney and Bird, ranging from single-language text (Wikipedia) to parallel text (UDHR and Omniglot) to IGTs (ODIN).  Table~\ref{table:corpus} gives some coverage statistics, and we describe each source in the following subsections.

\begin{table}[t]
\small
\centering
    \begin{tabular}{l|rr|rr}
    ~         				& Langs. 	& Families 	& Tokens		& Size	\\ \hline
    ODIN      				& 1,217      & 101       		& 58,556		& 39 MB		\\
    Omniglot  				& 134        & 21        		&	6,749			& 677 KB	\\
    UDHR      				& 355        & 47        		&	33,117		& 5.2 MB	\\
    Wikipedia 				& 209        & 22       		&						& 37 GB		\\ \hline
    \textbf{Combined}	& 1,347			 & 106 
    \end{tabular}
\caption{Corpus Coverage}
\label{table:corpus}
\end{table}

>>>>

\textbf{Analysed} texts, in addition to the raw text, contain more detailed annotations including parts of speech, morphological information, and syntactic relations.  This is stored as a table, where rows represent words, and columns represent the following types of information: document ID, language code, sentence ID, word ID, wordform, lemma, morphological information, part of speech, gloss, head/governor, and relation/role.

@@

Our resulting corpus runs the full gamut of text types outlined by Abney and Bird, ranging from single-language text (Wikipedia) to parallel text (UDHR and Omniglot) to IGTs (ODIN). For 332 languages the corpus contains data from more than one source.  Table~\ref{table:corpus} gives some coverage statistics, and we describe each source in the following subsections.

\begin{table}[t]
\small
\centering
    \begin{tabular}{l|rr|rr}
    ~         				& Langs. 	& Families 	& Tokens		& Size	\\ \hline
    ODIN      				& 1,270      & 100       		& 58,556		& 39 MB		\\
    Omniglot  				& 129        & 20        		& 6,749		& 677 KB	\\
    UDHR      				& 352        & 46        		& 33,117		& 5.2 MB	\\
    Wikipedia 				& 271        & 21       		&				& 37 GB\\ \hline
    \textbf{Combined}	    & 1,451	    & 105 
    \end{tabular}
\caption{Corpus Coverage}
\label{table:corpus}
\end{table}
